### 2013-05-18 article.tex
Fix address line for publication
Signed-off-by: Michael Barton <mail@michaelbarton.me.uk>
Remove acknowledgements for publication
Signed-off-by: Michael Barton <mail@michaelbarton.me.uk>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Genomer - a Swiss army knife for genome scaffolding.}
}
% Insert Author names, affiliations and corresponding author email.
\\
Michael D. Barton$^{1\ast}$, 
Hazel A. Barton$^{1}$
\\
\bf{1} Biology Department, The University of Akron, Akron, OH, 44325-3908, USA
\\
$\ast$ E-mail: mail@michaelbarton.me.uk
\end{flushleft}

@@

This work was supported by the National Institute for Health: IDeA Network of
Biomedical Research Excellence (KY-INBRE) grant (NIH 2P20 RR016481-09) and the
NIH R15 AREA Program grant (R15GM079775).

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Genomer - a Swiss army knife for genome scaffolding.}
}
% Insert Author names, affiliations and corresponding author email.
\\
Michael D. Barton$^{1\ast}$, 
Hazel A. Barton$^{1}$
\\
\bf{1} Biology Department, The University of Akron, Akron, OH, USA.
\\
$\ast$ E-mail: mail@michaelbarton.me.uk
\end{flushleft}

@@
